
```{r}
install.packages('MplusAutomation')
install.packages('xlsx')
```


```{r}
library(MplusAutomation)
library(dplyr)
library(xlsx)
```


Complete FDR corrections 
```{r}
#ATTN: This is based on how variables were named in the scripts of the present study. Double check your naming conventions
letter = c("G","A","E","I")

for( item in letter){
  variable1 =paste0("RI",item,".WITH")
  variable2 = "RIPTOTAL"
  
  #Grabs the first letter of the psychopathology dimension for naming purposes
  if(item == "G"){
    
    #Reads model - Change based on your script name if applicable
    modelResults <- readModels("Basic_General.out") 
    
    # read standardized results
    standardizedResults <- modelResults[["parameters"]][["stdyx.standardized"]]
    
    # read the index of regression results (can find in "paramHeader" column ending in ".ON")
    RI=grep(variable1,standardizedResults$paramHeader)
    I=grep(variable2, standardizedResults$param)
    
    RegI=intersect(RI, I)
    
    #create dataframe to store  data
    General <- data.frame(
      name = "general",
      est = standardizedResults$est[RegI],
      se = standardizedResults$se[RegI],
      est_se = standardizedResults$est_se[RegI],
      pval = standardizedResults$pval[RegI],
      stringsAsFactors = FALSE)
    
  }else if (item == "A"){
    #Reads model
    modelResults <- readModels("Basic_ADHD.out") 
    
    # read standardized results
    standardizedResults <- modelResults[["parameters"]][["stdyx.standardized"]]
    
    # read the index of regression results (can find in "paramHeader" column ending in ".ON")
    RI=grep(variable1,standardizedResults$paramHeader)
    I=grep(variable2, standardizedResults$param)
    
    RegI=intersect(RI, I)
    
    #create dataframe to store  data
    ADHD <- data.frame(
      name = "adhd",
      est = standardizedResults$est[RegI],
      se = standardizedResults$se[RegI],
      est_se = standardizedResults$est_se[RegI],
      pval = standardizedResults$pval[RegI],
      stringsAsFactors = FALSE)
    
    
    
  }else if(item == "E"){
    #Reads model
    modelResults <- readModels("Basic_Ext.out") 
    
    # read standardized results
    standardizedResults <- modelResults[["parameters"]][["stdyx.standardized"]]
    
    # read the index of regression results (can find in "paramHeader" column ending in ".ON")
    RI=grep(variable1,standardizedResults$paramHeader)
    I=grep(variable2, standardizedResults$param)
    
    RegI=intersect(RI, I)
    
    #create dataframe to store  data
    Ext <- data.frame(
      name = "ext",
      est = standardizedResults$est[RegI],
      se = standardizedResults$se[RegI],
      est_se = standardizedResults$est_se[RegI],
      pval = standardizedResults$pval[RegI],
      stringsAsFactors = FALSE)
    
  }else if (item == "I"){
    
    #Reads model
    modelResults <- readModels("Basic_Int.out") 
    
    # read standardized results
    standardizedResults <- modelResults[["parameters"]][["stdyx.standardized"]]
    
    # read the index of regression results (can find in "paramHeader" column ending in ".ON")
    RI=grep(variable1,standardizedResults$paramHeader)
    I=grep(variable2, standardizedResults$param)
    
    RegI=intersect(RI, I)
    
    #create dataframe to store  data
    Int <- data.frame(
      name = "int",
      est = standardizedResults$est[RegI],
      se = standardizedResults$se[RegI],
      est_se = standardizedResults$est_se[RegI],
      pval = standardizedResults$pval[RegI],
      stringsAsFactors = FALSE)
    
  }
}

all <- rbind(General,ADHD, Ext,Int)
all.p <- unlist(all[5])
all[6] <- round(p.adjust(all.p, method="fdr"),3)

colnames(all)[6] <- c("p_fdr")


df.RIX.WITH.RIPTOTAL <- all



```


Repeat for all (X is a placeholder for variable names corresponding to the four dimension, in our case G,A,E,I)
RI WITH RIPTotal - Between persons psychopathology and prosociality
WXB.WITH WPTOTALB - Within Persons psychopathology and prosociality
WX1.ON WXB -  psychopathology baseline to psychopathology year 1
WX2.ON WX1  -  psychopathology year 1 to psychopathology year 2
WPTOTAL1.ON WPTOTALB - prosocial baseline to prosocial year 1
WPTOTAL2.ON WPTOTAL1 - prosocial year 1 to prosocial year 2
WX1.ON WPTOTALB - cross lagged prosocial baseline to psychopathology year 1
WX2.ON WPTOTAL1 - cross lagged prosocial year 1 to psychopathlogy year 2 
WPTOTAL1.ON WXB - cross lagged psychopathology baseline to prosocial year 1
WPTOTAL2.ON WX1 - cross lagged psychopathology year 1 to prosocial year 2
